High-Dimensional Regularized Discriminant Analysis

### 2017-10-19 reports/title-page.tex
updated title page

\documentclass[review,authoryear]{elsarticle}
\usepackage{url}

%----------------Page dimensions ----------------
  \oddsidemargin 0.0in
\evensidemargin 0.0in
\topmargin -0.75in
\leftmargin 0in
\headheight 0.0in
\headsep 0.5in
\footskip 0.5in
\footnotesep 0.0in
\textwidth 6.5in
\textheight 9.5in

@@

\begin{frontmatter}

\title{High-Dimensional Regularized Discriminant Analysis}

\author[jar]{John A. Ramey}
\author[cks]{Caleb K. Stein}
\author[pdy]{Phil D. Young}
\author[dmy]{Dean M. Young}
\address[jar]{\textbf{Corresponding Author} \\ Novi Labs \\ 7020 Easy Wind Drive, Suite 210 \\ Austin, TX 78752 \\ USA \\ Email: johnramey@gmail.com}
\address[cks]{Myeloma Institute \\ University of Arkansas for Medical Sciences \\ 4018 W. Capitol Avenue \\ Little Rock, AR 72205 \\ USA \\ Email: stein.caleb@gmail.com}
\address[pdy]{Department of Management and Information Systems \\ Baylor University \\ One Bear Place \#98005 \\ Waco, TX 76798-8005 \\ USA \\ Email: Philip\_Young@baylor.edu}
\address[dmy]{Department of Statistical Science \\ Baylor University \\ P.O. Box 97140 \\ Waco, TX 76798-7140 \\ USA \\ Email: Dean\_Young@baylor.edu}

\end{frontmatter}

>>>>

\documentclass[]{interact}
\usepackage{url}

@@

\articletype{Title Page}
\title{High-Dimensional Regularized Discriminant Analysis}

\author{
\name{John A. Ramey\textsuperscript{a}\thanks{CONTACT John A. Ramey. Email: johnramey@gmail.com}, Caleb K. Stein\textsuperscript{b}, Phil D. Young\textsuperscript{c}, and Dean M. Young\textsuperscript{d}}
\affil{\textsuperscript{a}Novi Labs, Austin, TX, USA;\\ \textsuperscript{b}Myeloma Institute, University of Arkansas for Medical Sciences, Little Rock, AR, USA;\\ \textsuperscript{c}Department of Management and Information Systems, Baylor University, Waco, TX, USA;\\ \textsuperscript{d}Department of Statistical Science, Baylor University, Waco, TX, USA}
}

\maketitle
